### 2021-03-04 paper3/appendix.tex
Make it compile with the 3rd paper

\subsubsection{Adult Income}\label{ssec:dataset-construction-adult}
For the Adult Income dataset, we do not need to apply any synthetic biasing as the dataset naturally contains some bias wrt $s$. Thus, we instantiate the deployment set as just a random subset of the original dataset. Explicit balancing of the test set is needed to yield meaningful evaluation, however, namely in the penalizing of biased classifiers, but need be taken in doing so. Balancing the test set such that
\begin{align}
    |\{x \in X |s=0, y=0\}| &= |\{x \in X |s=1, y=0\}|    \nonumber\\
    \text{and}~|\{x \in X |s=0, y=1\}| &= |\{x \in X |s=1, y=1\}|
\end{align}
where for both target classes, $y=0$ and $y=1$, the proportions of the groups $s=0$ and $s=1$ are made to be the same, is intuitive, yet at the same time precludes sensible comparison of the accuracy/fairness trade-off of the different classifiers.
Indeed, with the above conditions, a majority classifier (predicting all 1s or 0s) achieves comparable accuracy to the fairness-unaware baselines, while also yielding perfect fairness, by construction.
This observation motivated us to devise an alternative scheme, where we balance the test set according to the following constraints
\begin{align}
    & |\{x \in X |s=0, y=0\}| 
    = |\{x \in X |s=0, y=1\}|  \nonumber \\
    = &|\{x \in X |s=1, y=1\}|
    = |\{x \in X |s=1, y=0\}|~.
 \end{align}
That is, all subsets of $\Scal \times \Ycal$ are made to be equally sized. Under this new scheme the accuracy of the the majority classifier is 50\% for the binary-classification task.

\subsection{Optimization}
\begin{table*}[p]
 \centering
 \caption{Selected hyperparameters for experiments with Coloured MNIST, Adult and CelebA datasets.}
 \label{tab:hparams}
 \begin{tabular}{llll}
 \toprule
 & \textbf{Coloured MNIST} & \textbf{Adult} & \textbf{CelebA}       
 \\ & 2-dig SB / 2-dig MS / 3-dig SB
 \\ \midrule
 Input size  &   $3 \times 32 \times 32$ & $61$ & $3 \times 64 \times 64$ \\  \midrule
 \multicolumn{4}{c}{Autoencoder}                     \\ \midrule
 Levels                      & $4$         & $1$    & $5$\\
 Level depth                 & $2$         & $1$    & $2$\\
 Hidden units / level        & $[32, 64, 128, 256]$ & $[61]$ & $[32, 64, 128, 256, 512]$\\
 Activation                  & GELU        & GELU   & GELU   \\
 Downsampling op.  & Strided Convs. & -- & Strided Convs.\\
 Reconstruction loss         & MSE         & Mixed$^1$  & MSE \\
 Learning rate               & $1 \times 10^{-3}$   & $1 \times 10^{-3}$  & $1 \times 10^{-3}$ \\ \midrule
 \multicolumn{4}{c}{Clustering}                      \\ \midrule
 Batch size                  & $256$      & $1000$  & --\\
 AE pre-training epochs      & $150$        & $100$ & --   \\
 Clustering epochs           & $100$       & $300$  & -- \\
 Self-supervised loss & Cosine + BCE & Cosine + BCE & --\\
 U (for ranking statistics)             & $5$         & $3$     & --    \\   \midrule
 \multicolumn{4}{c}{Distribution Matching}                   \\ \midrule
 Batch size & $1$/$32$/$14$  & $64$   & $32$ \\
 Bag size   & $256$/$8$/$18$ & $32$ & $8$ \\
 Training iterations    & $8\text{k}/8\text{k}/20\text{k}$ & $5\text{k}$ & $15\text{k}$ \\
 Encoding ($z$) size$^2$  & $128$   & $35$  & $128$ \\
 Binarised $z_s$ & \xmark\, / \cmark\, / \cmark & \xmark & \xmark \\
 $y$-predictor weight ($\lambda_1$) & $1$ & $0$ & $1$  \\ 
 $s$-predictor weight ($\lambda_2$) & $1$ & $0$ & $0$  \\ 
 Adversarial weight ($\lambda_3$)   & $1 \times
 10^{-3}$   & $1$   & $1$\\ 
 Stopgradient $\left(\nabla_\theta h_\psi(f_\theta(X^\mathit{dep}))=0\right)$ & \xmark & \cmark & \xmark \\
 \midrule
 \multicolumn{4}{c}{Predictors}   \\ \midrule
 Learning rate  & $3 \times 10^{-4}$ &   $1 \times 10^{-3}$  $ 1 \times 10^{-3}$\\
 \midrule
 \multicolumn{4}{c}{Discriminator}                   \\ \midrule
 Attention mechanism$^3$    & Gated   & Gated & Gated \\
 Hidden units pre-aggregation  & $[256, 256]$  & $[32]$ & $[256, 256]$\\
 Hidden units post-aggregation & $[256, 256]$ & --  & $[256, 256]$ \\
 Embedding dim (for attention) & $32$ & $128$ & $128$ \\
 Activation & GELU & GELU & GELU \\
 Learning rate  & $3 \times 10^{-4}$    & $1 \times 10^{-3}$ & $1 \times 10^{-3}$\\
 Updates / AE update    & $1$  & $3$    & $1$    \\
 \bottomrule
 \multicolumn{4}{l}{\footnotesize $^1$ Cross-entropy is used for categorical features, MSE for continuous features.} \\
  \multicolumn{4}{p{\textwidth}}{\footnotesize $^2$ $|z|$ denotes the combined size of $z_s$ and $z_y$, with the former occupying $\ceil{\text{log}_2(\mathcal{S})}$ dimensions, the latter the remaining } \\
  \multicolumn{4}{p{\textwidth}}{\footnotesize dimensions.} \\
  \multicolumn{4}{p{\textwidth}}{\footnotesize $^3$ The attention mechanism used for computing the sample-weights within a bag. \emph{Gated} refers to gated attention  proposed by
%   \cite{ilse2018attention}, while \emph{SDP} refers to the scaled dot-product attention proposed by \cite{vaswani2017attention}.
  } \\ 
  \multicolumn{4}{p{\textwidth}}{\footnotesize  \cite{ilse2018attention}.} \\ 
 \end{tabular}
\end{table*}

@@

\subsection{Visualizations of results}\label{sec:qual-results}
Figures~\ref{fig:attn_maps} and \ref{fig:cmnist-recon} show some additional visualizations for our results.
For details, see the captions.
\begin{figure*}[tb]
  \centering
    \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{figures/celeba_attn_map.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{figures/cmnist_attn_map.png}
    \end{subfigure}
  \caption{
    Example sample-wise attention maps for bags of CelebA (left) and Coloured MNIST (right) images sampled from a balanced deployment set. The training set is biased according to the SB setting where for CelebA ``smiling females'' constitute the missing source and for Colored MNIST {\color{purple}purple} fours constitute the missing source. The attention weights are used during the discriminator's aggregation step to compute a weighted sum over the bag. The attention-weight assigned to each sample is proportional to the lightness of its frame, with black signifying a weight of 0, white a weight of 1. Those samples belonging to the missing subgroup are assigned the highest weight as they signal from which dataset (training vs. deployment) the bag containing them was drawn from.
  }%
  \label{fig:attn_maps}
\end{figure*}

>>>>

\subsubsection{Adult Income}\label{ssec:dataset-construction-adult}
For the Adult Income dataset, we do not need to apply any synthetic biasing as the dataset naturally contains some bias wrt $s$. Thus, we instantiate the deployment set as just a random subset of the original dataset. Explicit balancing of the test set is needed to yield meaningful evaluation, however, namely in the penalizing of biased classifiers, but need be taken in doing so. Balancing the test set such that
\begin{align}
    |\{x \in X |s=0, y=0\}| &= |\{x \in X |s=1, y=0\}|    \nonumber\\
    \text{and}~|\{x \in X |s=0, y=1\}| &= |\{x \in X |s=1, y=1\}|
\end{align}
where for both target classes, $y=0$ and $y=1$, the proportions of the groups $s=0$ and $s=1$ are made to be the same, is intuitive, yet at the same time precludes sensible comparison of the accuracy/fairness trade-off of the different classifiers.
Indeed, with the above conditions, a majority classifier (predicting all 1s or 0s) achieves comparable accuracy to the fairness-unaware baselines, while also yielding perfect fairness, by construction.
This observation motivated us to devise an alternative scheme, where we balance the test set according to the following constraints
\begin{align}
    & |\{x \in X |s=0, y=0\}| 
    = |\{x \in X |s=0, y=1\}|  \nonumber \\
    = &|\{x \in X |s=1, y=1\}|
    = |\{x \in X |s=1, y=0\}|~.
 \end{align}
That is, all subsets of $\gS \times \gY$ are made to be equally sized. Under this new scheme the accuracy of the the majority classifier is 50\% for the binary-classification task.

\subsection{Optimization}
\begin{table*}[p]
 \centering
 \caption{Selected hyperparameters for experiments with Coloured MNIST, Adult and CelebA datasets.}
 \label{tab:hparams}
 \begin{tabular}{llll}
 \toprule
 & \textbf{Coloured MNIST} & \textbf{Adult} & \textbf{CelebA}       
 \\ & 2-dig SB / 2-dig MS / 3-dig SB
 \\ \midrule
 Input size  &   $3 \times 32 \times 32$ & $61$ & $3 \times 64 \times 64$ \\  \midrule
 \multicolumn{4}{c}{Autoencoder}                     \\ \midrule
 Levels                      & $4$         & $1$    & $5$\\
 Level depth                 & $2$         & $1$    & $2$\\
 Hidden units / level        & $[32, 64, 128, 256]$ & $[61]$ & $[32, 64, 128, 256, 512]$\\
 Activation                  & GELU        & GELU   & GELU   \\
 Downsampling op.  & Strided Convs. & -- & Strided Convs.\\
 Reconstruction loss         & MSE         & Mixed$^1$  & MSE \\
 Learning rate               & $1 \times 10^{-3}$   & $1 \times 10^{-3}$  & $1 \times 10^{-3}$ \\ \midrule
 \multicolumn{4}{c}{Clustering}                      \\ \midrule
 Batch size                  & $256$      & $1000$  & --\\
 AE pre-training epochs      & $150$        & $100$ & --   \\
 Clustering epochs           & $100$       & $300$  & -- \\
 Self-supervised loss & Cosine + BCE & Cosine + BCE & --\\
 U (for ranking statistics)             & $5$         & $3$     & --    \\   \midrule
 \multicolumn{4}{c}{Distribution Matching}                   \\ \midrule
 Batch size & $1$/$32$/$14$  & $64$   & $32$ \\
 Bag size   & $256$/$8$/$18$ & $32$ & $8$ \\
 Training iterations    & $8\text{k}/8\text{k}/20\text{k}$ & $5\text{k}$ & $15\text{k}$ \\
 Encoding ($z$) size$^2$  & $128$   & $35$  & $128$ \\
 Binarised $z_s$ & {\boxedsymbols ✗}\, / \cmark\, / \cmark & \xmark & \xmark \\
 $y$-predictor weight ($\lambda_1$) & $1$ & $0$ & $1$  \\ 
 $s$-predictor weight ($\lambda_2$) & $1$ & $0$ & $0$  \\ 
 Adversarial weight ($\lambda_3$)   & $1 \times
 10^{-3}$   & $1$   & $1$\\ 
 Stopgradient $\left(\nabla_\theta h_\psi(f_\theta(X^\mathit{dep}))=0\right)$ & \xmark & \cmark & \xmark \\
 \midrule
 \multicolumn{4}{c}{Predictors}   \\ \midrule
 Learning rate  & $3 \times 10^{-4}$ &   $1 \times 10^{-3}$  $ 1 \times 10^{-3}$\\
 \midrule
 \multicolumn{4}{c}{Discriminator}                   \\ \midrule
 Attention mechanism$^3$    & Gated   & Gated & Gated \\
 Hidden units pre-aggregation  & $[256, 256]$  & $[32]$ & $[256, 256]$\\
 Hidden units post-aggregation & $[256, 256]$ & --  & $[256, 256]$ \\
 Embedding dim (for attention) & $32$ & $128$ & $128$ \\
 Activation & GELU & GELU & GELU \\
 Learning rate  & $3 \times 10^{-4}$    & $1 \times 10^{-3}$ & $1 \times 10^{-3}$\\
 Updates / AE update    & $1$  & $3$    & $1$    \\
 \bottomrule
 \multicolumn{4}{l}{\footnotesize $^1$ Cross-entropy is used for categorical features, MSE for continuous features.} \\
  \multicolumn{4}{p{\textwidth}}{\footnotesize $^2$ $|z|$ denotes the combined size of $z_s$ and $z_y$, with the former occupying $\ceil{\text{log}_2(\mathcal{S})}$ dimensions, the latter the remaining } \\
  \multicolumn{4}{p{\textwidth}}{\footnotesize dimensions.} \\
  \multicolumn{4}{p{\textwidth}}{\footnotesize $^3$ The attention mechanism used for computing the sample-weights within a bag. \emph{Gated} refers to gated attention  proposed by
%   \cite{ilse2018attention}, while \emph{SDP} refers to the scaled dot-product attention proposed by \cite{vaswani2017attention}.
  } \\ 
  \multicolumn{4}{p{\textwidth}}{\footnotesize  \cite{ilse2018attention}.} \\ 
 \end{tabular}
\end{table*}

@@

\subsection{Visualizations of results}\label{sec:qual-results}
Figures~\ref{fig:attn_maps} and \ref{fig:cmnist-recon} show some additional visualizations for our results.
For details, see the captions.
\begin{figure*}[tb]
  \centering
    % \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{figures/celeba_attn_map.png}
    % \end{subfigure}
    % \hfill
    % \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{figures/cmnist_attn_map.png}
    % \end{subfigure}
  \caption{
    Example sample-wise attention maps for bags of CelebA (left) and Coloured MNIST (right) images sampled from a balanced deployment set. The training set is biased according to the SB setting where for CelebA ``smiling females'' constitute the missing source and for Colored MNIST {\color{purple}purple} fours constitute the missing source. The attention weights are used during the discriminator's aggregation step to compute a weighted sum over the bag. The attention-weight assigned to each sample is proportional to the lightness of its frame, with black signifying a weight of 0, white a weight of 1. Those samples belonging to the missing subgroup are assigned the highest weight as they signal from which dataset (training vs. deployment) the bag containing them was drawn from.
  }%
  \label{fig:attn_maps}
\end{figure*}
